% LaTeX file for resume

% possible options include:
%   font size (10pt, 11pt and 12pt)
%   paper size (a4paper, a5paper, letterpaper, legalpaper, and landscape)
%   font family (sans and roman)
\documentclass[10pt,letterpaper,sans]{moderncv}

% style options are casual (default), classic, banking, oldstyle and fancy
% color options black, blue (default), burgundy, green, grey, orange, and red
\moderncvstyle{casual}
\moderncvcolor{blue}
%\moderncvicons{marvosym}

% Disable page numbers
\nopagenumbers{}

% character encoding
\usepackage[utf8]{inputenc}

% adjust the page margins
\usepackage[scale=0.75]{geometry}

% if you want to change the width of the column with the dates
%%\setlength{\hintscolumnwidth}{3cm}

% if you want to force the width allocated to your name and avoid line breaks
%%\setlength{\makecvtitlenamewidth}{10cm}

\name{Alice}{McKean}
\email{mckeankylej@gmail.com}
\social[github]{aljce}
\phone{+1 770 335 0640}

\newcommand{\wlink}[2]{\textcolor[HTML]{0020B6}{\href{#1}{#2}}}
\newcommand{\lang}[1]{\texttt{#1}}

\newcommand{\ghlink}[2]{\wlink{https://github.com/#1}{#2}}
\newcommand{\ghrepo}[1]{\ghlink{#1}{\faGithub}}
\newcommand{\ghlang}[1]{\texttt{#1}}
\newcommand{\ghcom}[1]{\textcolor[HTML]{666666}{\ghCommit{} #1}}
\newcommand{\ghadd}[1]{\textcolor[HTML]{30A622}{{\faPlusCircle} #1}}
\newcommand{\ghrem}[1]{\textcolor[HTML]{BD2C00}{{\faMinusCircle} #1}}
\newcommand{\ghtf}[0]{\faCodeFork}

\newcommand{\ghub}[4]{\ghrepo{#2} | \ghlang{#1} | \ghadd{#3} | \ghrem{#4}}

\begin{document}
\makecvtitle{}

\section{Work Experience}

\cventry
{2020--Present}
{Software + Infrastructure Engineer}
{\wlink{https://mercury.co/}{Mercury Bank}}
{}{}
{
  \begin{itemize}         
  \item Managed an entire AWS stack with nix autodeploys that ran through Hydra.
  \item Oversaw the migration to 100\% infrastructure as code via terraform.
  \item Personally handled complex Postgres upgrades that required planned downtime.
  \item Migrated the company to a new VPN that allowed for finer access controls
    for our admins.
  \item Added structured logging to the backend via Elasticsearch.
  \item \ghub{Haskell + Nix + Terraform}{mercury-technologies}{27165}{24032}
  \end{itemize}
}


\cventry{Summer 2019}
        {Software Engineering Intern}
        {\wlink{https://mercury.co/}{Mercury Bank}}
        {}{}
        {
\begin{itemize}         
\item Developed 12+ third party bank integrations.
\item Improved fraud detection for domestic wires.
\item \ghub{Haskell}{mercury-technologies}{3049}{474}
\end{itemize}
}

\cventry{2016--2017}
        {Software Engineer}
        {\wlink{http://layer3com.com/}{Layer 3 Communications}}
        {}{}
        {
\begin{itemize}
\item Co-authored a network threat analysis application in \lang{Haskell}.
\item The application collected, parsed, enriched, and correlated 80,000 logs
  a second.
\item I managed the deployment to Atlanta City Government (10GB of logs a day).
\item Orchestrated the Elasticsearch cluster and Postgres instance.
\item \ghub{Haskell}{layer-3-communications}{18029}{17186}
\end{itemize}
}

\cventry{Summer 2016}
        {Software Engineering Intern}
        {\wlink{http://layer3com.com/}{Layer 3 Communications}}
        {}{}
        {
\begin{itemize}
\item Developed a log collection and analytics tool in \lang{Haskell}.
\item Then managed the deployment of said application to 100+ client boxes with \lang{Nix}.
\item \ghub{Haskell}{layer-3-communications}{6052}{3415}
\end{itemize}
}

\section{Education}
\cventry
{2017--2020}
{BS, Computer Science}
{\wlink{https://reed.edu}{Reed College}}
{Portland, OR}
{}
{}

\section{Undergraduate Thesis}
\cventry
{2019--2020}
{A Replication of the AKS Primality Decision Algorithm}
{}
{}
{}
{
  \begin{itemize}         
  \item Developed a formalization of the AKS primality decision algorithm in the Agda proof assistant.
  \item Included expository sections describing how to formalize non trivial proofs in Agda.
  \item \ghub{Agda}{aljce/thesis}{3152}{565}
  \end{itemize}
}

\section{Extracurricular}
\cventry{2017--2020}
{Lecture}
{\wlink{http://reed.edu}{Reed College} Math Colloquium}
{}{}{
  \begin{itemize}
  \item Formalizing the metatheory of bidirectional type theory
  \item Lambda Calculus as a foundation of computability theory
  \end{itemize}
}

\section{Skills}
\cvitem{Languages}{
  \href{https://en.wikipedia.org/wiki/Haskell_(programming_language)}{\lang{Haskell}} (9 yrs),
  \href{https://en.wikipedia.org/wiki/Nix_package_manager}{\lang{Nix}} (6 yrs), %
  \href{https://en.wikipedia.org/wiki/Terraform_(software)}{\lang{Terraform}}, %
  \href{https://en.wikipedia.org/wiki/SQL}{\lang{SQL}}, %
  \href{https://en.wikipedia.org/wiki/Java_(programming_language)}{\lang{Java}}, %
  \href{https://en.wikipedia.org/wiki/Python_(programming_language)}{\lang{Python}}, %
  \href{https://en.wikipedia.org/wiki/TypeScript}{\lang{TypeScript}}%
}
\cvitem{Software}{%
  \href{https://en.wikipedia.org/wiki/Linux}{Linux} (10 yrs), %
  \href{https://debian.org}{Debian}, %
  \href{https://nixos.org}{NixOS}, %
  \href{https://aws.amazon.com}{AWS}, %
  \href{https://postgresql.org}{PostgreSQL}, %
  \href{https://git-scm.com}{git}, %
  \href{https://www.latex-project.org}{\LaTeX} %
}

\end{document}
